Carbonate chemistry at Ny-Ålesund

### 2023-06-02 awipev-CO2.Rmd
Time spent at each depth group Various updates in figures for ESSD

## Stratification

### Stratification salinity

@@

# First create the tibble
depth_labels <- c("0-2", "2-4", "4-6", "6-8", ">8")
tmp <- d_all %>% 
  dplyr::select(datetime, depth_group) %>%
  dplyr::filter(depth_group != "NA") %>% 
  dplyr::mutate(depth_group = factor(depth_group, levels = depth_labels))

count_depth <- depth_time(tmp) 
plot_all_depths <- count_depth %>% 
  ggplot() +
  geom_bar(aes(x=hours_spent))
plot_all_depths
```

```{r, echo=FALSE, message= FALSE, warning=FALSE}
size_labs = 14
# we look at the distribution of data
depth_labels <- c("0-2", "2-4", "4-6", "6-8", ">8")
# we look at salinity all depths
tmp <- d_all %>% 
  dplyr::select(montht, sal_insitu_ctd, depth_group) %>%
  dplyr::filter(depth_group != "NA") %>% 
  dplyr::mutate(depth_group = factor(depth_group, levels = depth_labels))
p <- tmp %>% 
  ggplot(aes(x=as.factor(depth_group), y = sal_insitu_ctd)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "Salinity vs depth", x = "Depth (m)", y= "Salinity") +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
summary(aov(tmp$sal_insitu_ctd ~ tmp$depth_group * tmp$montht))

@@

ts_sal <- d_all %>%
  ggplot(aes(x = datetime, y = sal_fb_mix), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  labs(title="A",x=NULL, y="Salinity") +
  scale_y_continuous(limits = c(31.8, 35.5)) +
  Mytheme(size_labs = size_labs) +
  theme(#axis.title.x = element_text(face = "bold", size = size_labs),
        axis.title.y = element_text(face = "bold", size = size_labs),
        axis.text.x=element_blank(),
        title = element_text(colour="black", size=14, face="bold"),
         axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        )

@@

# identify extremes
d_bp <- d_bp %>%
  dplyr::mutate(
    ext_sal_fb_mix = ifelse(
      sal_fb_mix < dec_sal_fb_mix[1] |
        sal_fb_mix > dec_sal_fb_mix[2],
      sal_fb_mix,
      NA
    ),
    ext_temp_insitu_11m = ifelse(
      temp_insitu_11m < dec_temp_insitu_11m[1] |
        temp_insitu_11m > dec_temp_insitu_11m[2],
      temp_insitu_11m,
      NA
    ),
    ext_pco2_fb = ifelse(pco2_fb < dec_pco2_fb[1] |
                           pco2_fb > dec_pco2_fb[2], pco2_fb, NA),
    ext_pHint_tot_sf = ifelse(
      pHint_tot_sf < dec_pHint_tot_sf[1] |
        pHint_tot_sf > dec_pHint_tot_sf[2],
      pHint_tot_sf,
      NA
    ),
    ext_at_calc = ifelse(at_calc < dec_at_calc[1] |
                           at_calc > dec_at_calc[2], at_calc, NA)
  )
ts_sal_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb_mix)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb_mix), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="F", y = NULL, x=NULL) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        # axis.title.x = element_text(face = "bold", size = size_labs),
        # label.x = element_text(face = "bold", size = size_labs),
        # axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        ) #+
  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  # scale_y_continuous(limits = c(31.8, 35.5))

ts_temp_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = temp_insitu_11m)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_temp_insitu_11m), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="G", y = NULL, x=NULL) +
  scale_y_continuous(limits = c(-1.8, 8)) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        # axis.title.x = element_text(face = "bold", size = size_labs),
        # label.x = element_text(face = "bold", size = size_labs),
        # axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        ) #+
  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))

ts_pco2_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pco2_fb)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pco2_fb), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="H", y = NULL, x=NULL) +
  scale_y_continuous(limits = c(180, 400)) +
  Mytheme(size_labs = size_labs)+
  theme(panel.grid.major.x = element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        # axis.title.x = element_text(face = "bold", size = size_labs),
        # label.x = element_text(face = "bold", size = size_labs),
        # axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        ) #+
  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
ts_pH_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pHint_tot_sf)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pHint_tot_sf), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="I", y = NULL, x=NULL) +
  scale_y_continuous(limits = c(7.99, 8.2)) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        # axis.title.x = element_text(face = "bold", size = size_labs),
        # label.x = element_text(face = "bold", size = size_labs),
        # axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        ) #+
  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))

ts_at_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = at_calc)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_at_calc), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="J", y = NULL, x="Month") +
  scale_y_continuous(limits = c(2135, 2355)) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        #axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.title.x = element_text(face = "bold", size = size_labs),
        #axis.label.x = element_text(face = "bold", size = size_labs),
        # axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        ) +
  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
# Combine plots
g2 <- (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
g2 <- g2 + plot_annotation(tag_levels = 'A') & 
                             theme(plot.tag = element_text(face = "bold"))
ggsave(filename = "figures/ts_boxplots.png", plot = g2, width = 12)
```

>>>>

## Stratification {.tabset .tabset-pills}

### REMOS

@@

# First create the tibble
depth_labels <- c("0-2", "2-4", "4-6", "6-8", ">8")
tmp <- d_all %>% 
  dplyr::select(datetime, depth_group) %>%
#  dplyr::filter(depth_group != "NA") %>% 
  dplyr::mutate(depth_group = factor(depth_group, levels = depth_labels))

count_depth <- depth_time(tmp) %>% 
  dplyr::filter(depth_group != "NA")
p <- ggplot(count_depth) +
  geom_bar(aes(x=log10(hours_spent)))
ggsave(filename = "figures/REMOS.png", plot = p, width = 15, height = 10, units = "cm")

```
The REMOS spent a highly variable period of time in each depth group.
![Distribution of the number of hours spent by the REMOS at depth](figures/REMOS.png)
`r knitr::kable(summary(count_depth$hours_spent))`

### Stratification salinity
```{r, echo=FALSE, message= FALSE, warning=FALSE}
size_labs = 14
# we look at the distribution of data
depth_labels <- c("0-2", "2-4", "4-6", "6-8", ">8")
# we look at salinity all depths
tmp <- d_all %>% 
  dplyr::select(montht, sal_insitu_ctd, depth_group) %>%
  dplyr::filter(depth_group != "NA") %>% 
  dplyr::mutate(depth_group = factor(depth_group, levels = depth_labels))
p <- tmp %>% 
  ggplot(aes(x=as.factor(depth_group), y = sal_insitu_ctd)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "Salinity vs depth", x = "Depth (m)", y= "Salinity") +
  facet_wrap(vars(montht), scale = "free_y")
print(p)
summary(aov(tmp$sal_insitu_ctd ~ tmp$depth_group * tmp$montht))

@@

ts_sal <- d_all %>%
  ggplot(aes(x = datetime, y = sal_fb_mix), na.rm = TRUE) +
  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
  labs(title="A",x=NULL, y="Salinity (< 8 m)") +
  scale_y_continuous(limits = c(31.8, 35.5)) +
  Mytheme(size_labs = size_labs) +
  theme(#axis.title.x = element_text(face = "bold", size = size_labs),
        axis.title.y = element_text(face = "bold", size = size_labs),
        axis.text.x=element_blank(),
        title = element_text(colour="black", size=14, face="bold"),
         axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        )

@@

# identify extremes
d_bp <- d_bp %>%
  dplyr::mutate(
    ext_sal_fb_mix = ifelse(
      sal_fb_mix < dec_sal_fb_mix[1] |
        sal_fb_mix > dec_sal_fb_mix[2],
      sal_fb_mix,
      NA
    ),
    ext_temp_insitu_11m = ifelse(
      temp_insitu_11m < dec_temp_insitu_11m[1] |
        temp_insitu_11m > dec_temp_insitu_11m[2],
      temp_insitu_11m,
      NA
    ),
    ext_pco2_fb = ifelse(pco2_fb < dec_pco2_fb[1] |
                           pco2_fb > dec_pco2_fb[2], pco2_fb, NA),
    ext_pHint_tot_sf = ifelse(
      pHint_tot_sf < dec_pHint_tot_sf[1] |
        pHint_tot_sf > dec_pHint_tot_sf[2],
      pHint_tot_sf,
      NA
    ),
    ext_at_calc = ifelse(at_calc < dec_at_calc[1] |
                           at_calc > dec_at_calc[2], at_calc, NA)
  )
ts_sal_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb_mix)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb_mix), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="F", y = NULL, x=NULL) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        # axis.title.x = element_text(face = "bold", size = size_labs),
        # label.x = element_text(face = "bold", size = size_labs),
        # axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        )
# to change color of median line
tmp <- ggplot_build(ts_sal_bp)$data[[1]]
ts_sal_bp <- ts_sal_bp + geom_segment(data=tmp, aes(x=xmin, xend=xmax, 
                               y=middle, yend=middle), colour="cyan", size=1)

#+
  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  # scale_y_continuous(limits = c(31.8, 35.5))

ts_temp_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = temp_insitu_11m)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_temp_insitu_11m), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="G", y = NULL, x=NULL) +
  scale_y_continuous(limits = c(-1.8, 8)) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        # axis.title.x = element_text(face = "bold", size = size_labs),
        # label.x = element_text(face = "bold", size = size_labs),
        # axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        ) #+
  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
# to change color of median line
tmp <- ggplot_build(ts_temp_bp)$data[[1]]
ts_temp_bp <- ts_temp_bp + geom_segment(data=tmp, aes(x=xmin, xend=xmax, 
                               y=middle, yend=middle), colour="cyan", size=1)
ts_pco2_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pco2_fb)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pco2_fb), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="H", y = NULL, x=NULL) +
  scale_y_continuous(limits = c(180, 400)) +
  Mytheme(size_labs = size_labs)+
  theme(panel.grid.major.x = element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        # axis.title.x = element_text(face = "bold", size = size_labs),
        # label.x = element_text(face = "bold", size = size_labs),
        # axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        ) #+
  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
# to change color of median line
tmp <- ggplot_build(ts_pco2_bp)$data[[1]]
ts_pco2_bp <- ts_pco2_bp + geom_segment(data=tmp, aes(x=xmin, xend=xmax, 
                               y=middle, yend=middle), colour="cyan", size=1)

ts_pH_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pHint_tot_sf)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pHint_tot_sf), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="I", y = NULL, x=NULL) +
  scale_y_continuous(limits = c(7.99, 8.2)) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        # axis.title.x = element_text(face = "bold", size = size_labs),
        # label.x = element_text(face = "bold", size = size_labs),
        # axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        ) #+
  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
# to change color of median line
tmp <- ggplot_build(ts_pH_bp)$data[[1]]
ts_pH_bp <- ts_pH_bp + geom_segment(data=tmp, aes(x=xmin, xend=xmax, 
                               y=middle, yend=middle), colour="cyan", size=1)
ts_at_bp <- d_bp %>%
  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = at_calc)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_at_calc), col = "lightblue", size = size_point, na.rm = TRUE) +
  labs(title="J", y = NULL, x="Month") +
  scale_y_continuous(limits = c(2135, 2355)) +
  Mytheme(size_labs = size_labs) +
  theme(panel.grid.major.x = element_blank(),
        #axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.title.x = element_text(face = "bold", size = size_labs),
        #axis.label.x = element_text(face = "bold", size = size_labs),
        # axis.title.y = element_text(face = "bold", size = size_labs),
        title = element_text(colour="black", size=14, face="bold"),
        axis.ticks.length.y = unit(.2, "cm"),
        axis.ticks.length.x = unit(.2, "cm"),
        axis.ticks.x = element_line(size = 0.5),
        axis.ticks.y = element_line(size = 0.5)
        ) +
  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
# to change color of median line
tmp <- ggplot_build(ts_at_bp)$data[[1]]
ts_at_bp <- ts_at_bp + geom_segment(data=tmp, aes(x=xmin, xend=xmax, 
                               y=middle, yend=middle), colour="cyan", size=1)

# Combine plots
g2 <- (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
g2 <- g2 + plot_annotation(tag_levels = 'A') & 
                             theme(plot.tag = element_text(face = "bold"))
ggsave(filename = "figures/ts_boxplots.png", plot = g2, width = 12)
```
